% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage{url}
\usepackage{hanging}
\usepackage{parskip}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc, osf]{mathpazo}
%\usepackage{helvet}
%\renewcommand{\familydefault}{\sfdefault}

% Set your name here
\def\name{Ryan Mcginty Hynes}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {economics, statistics, mathematics},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.0in,
  bottom=1.0in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}

\begin{minipage}{0.45\linewidth}
  \href{http://http://www.ucd.ie/economics/}{University College Dublin} \\
  School of Economics \\
 Newman Building (G215) \\
 Belfield\\
 Dublin 4\\
 Ireland\\
 
\end{minipage}
\begin{minipage}{0.45\linewidth}
  \begin{tabular}{ll}
    Email: & \href{mailto:rhynes57@gmail.com}{\tt rhynes57@gmail.com} \\
    Homepage: & \href{http://ryanhynes.org}{\tt http://ryanhynes.org} \\
    Citizenship: & United States \\
  \end{tabular}
\end{minipage}

\section*{Research Interests}
\begin{itemize}
\item I am interested in the intersection of law, economics, and technology. Currently I focus on patents, both as policy instruments and data sources for innovation, migration, and competition. 
\end{itemize} 

\section*{Education}

\begin{itemize}
  \item Ph.D. Candidate, School of Economics, University College Dublin (UCD) 2017 -- Present.
  \item J.D. Chicago-Kent College of Law, 2015.
  \subitem Member, Illinois Bar 2015 -- Present.
  \item M.S. Finance, Illinois Institute of Technology (IIT), 2016.
  	\subitem Thesis: \emph{A Patent's Worth a Thousand Words:
Determining Patent Quality with Text
Classification}.
  \item B.S. Applied Economics, Illinois Institute of Technology, 2016.
  \item B.S. Finance, Illinois Institute of Technology, 2014.
  

  
\end{itemize}

\section*{Research}
\begin{itemize}
\item {\bf Current Projects}

\leftskip 0.5in
\parindent -0.5in
\subitem My Kind of Town: The effect of regional specialization on inventor location, with Bernardo Buarque, Ron Davies, and Dieter Kogler
\subitem The effect of patent box incentives on patent quality, with Ron Davies
\subitem Trade patent premia? The effect of innovation on price, with Ron Davies
\subitem My Kind of Town: Regional innovation networks and inventor migration
\subitem TRIPS Plus what? The effect of TRIPS-Plus patent provisions in CAFTA countries
\\


\leftskip 0in
\item {\bf Publications}
\subitem{\emph{OK Computer: The Creation and Integration of Artificial Intelligence in Europe} Cambridge Journal of Regions, Economy and Society, \emph{February 2020}}
\leftskip 0.5in
\parindent -0.5in

\subitem{\href{http://studentorgs.kentlaw.iit.edu/jicl/mexico-trucking-final-cc-2/}{\emph{The Truck Stops Here: The Impending Mexico-US Trucking Dispute} Chicago-Kent Journal of International and Comparative Law, January 2015}}
\leftskip 0.5in
\parindent -0.5in

\leftskip 0in

\pagebreak

\item {\bf Presentations}
\subitem{2019}
\begin{itemize}
\item{Summer School on Science, Technology and Innovation Studies, Vienna}
\item{European Trade Study Group, Bern}
\item{Regional Studies Association Europe Summer School, Cagliari}
\item{Munich Young Economists Meeting, Kochel am See}
\item{Society for International Trade Theory, Dublin}
\item{Economic Geography and International Trade, Vienna}
\end{itemize}
\subitem{2018}
\begin{itemize}
\item{Economic and Social Research Institute, Dublin}
\end{itemize}
\leftskip 0.5in
\parindent -0.5in

\end{itemize}


\section*{Professional Experience}
\begin{itemize}
\item{Software Engineer, Relativity ODA LLC, 2016 -- 2020}
\item{Assistant Counsel, Relativity ODA LLC, 2014 -- 2017}
\item{Application Analyst, kCura Corporation, 2012 -- 2014}
\end{itemize}


\section*{Teaching}
\begin{itemize}
\item {Lecturer:}
\subitem{\textbf{ECON20040:} Statistics for Economists, UCD (Spring 2020)}
\item {Teaching Assistant:}
\subitem{\textbf{ECON20040:} Statistics for Economists, UCD (Fall 2017, 2018)}
\subitem{\textbf{ECON30130:} Econometrics, UCD (Spring 2018, 2019)}
\subitem{\textbf{ECON30160:} International Trade, UCD (Spring 2018)}
\end{itemize}


\section*{Grants, Honors, and Awards}
\begin{itemize}
\item{\emph{UCD Graduate Scholarship}, UCD, 2017 -- Present.}
\item{\emph{Marvin Camras Scholarship}, IIT, 2011 -- 2016. }
\end{itemize}

\section*{Journals}
\begin{itemize}
\item {\bf Referee}
\subitem International Tax and Public Finance, 2020 - Present
\end{itemize}

\section*{Skills}
\begin{itemize}
\item {\bf Programming}
\subitem Chef, Jenkins, Powershell, Python, R, Ruby, STATA
\end{itemize}

% Footer
\begin{center}
  \begin{footnotesize}
    Last updated: \today \\
  \end{footnotesize}
\end{center}

\end{document}
